\tnoteref{note1}Training Feedforward Neural Networks with Bayesian Hyper-Heuristics

### 2024-08-15 article/main.tex
💚 For Taylah, Beané & Aleah

Although this research takes a particular interest in training \acp{FFNN}, the \acs{BHH} is not limited to these types of models and can generally be applied to any \acs{ANN} as long as the \acs{ANN} can be trained by all of the low-level heuristics. Experimentation with other \acp{ANN} architectures besides \acp{FFNN} is left for future research.

@@

This research focuses on a particular type of \acs{ANN}, referred to as \acfp{FFNN}. \acp{FFNN} were the first and simplest type of \acp{ANN} developed \citep{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order. Furthermore, \acp{FFNN} implement fully connected topologies, where each \acf{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles \citep{ref:zell:1994}. In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.

@@

There are many variants of gradient-based heuristics. However, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}. This algorithm is known as \acf{BP}, was popularised by \citet{ref:werbos:1994}.

@@

The biggest difference between \acp{MH} and gradient-based heuristics is that \acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space \citep{ref:blum:2003}. This also means that \acp{MH} do not necessarily require the error function to be differentiable. \citet{ref:blum:2003} provide advantages of \acp{MH} that include the following: they are easy to implement, they are problem independent and do not require problem-specific knowledge, and they are generally designed to find global optima, while gradient-based approaches can get stuck in local optima more often. Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \citep{ref:rakitianskaia:2012, ref:vanwyk:2014, ref:gupta:1999}. This research takes a particular interest in population-based \acp{MH} that have been used to train \acp{FFNN}. These include \acf{PSO} \citep{ref:abdulkarim:2021}, \acf{DE} \citep{ref:xue:2022}, and \acfp{GA} \citep{ref:khan:2012}.

@@

\citet{ref:burke:2010} propose a classification scheme used to classify \acp{HH}. According to the proposed classification scheme, \acp{HH} are classified in two dimensions. These include the \textit{source of feedback} used during learning and the nature of the \textit{heuristic search space}. For the dimension that involves the source of feedback, \acp{HH} can be classified as either \textit{no learning}, \textit{online learning} or \textit{offline learning}. For the dimension that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}. Further distinction is made between \textit{construction} of heuristics and \textit{perturbation} of heuristics.

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include \citep{ref:burke:2010, ref:dowsland:2007, ref:grobler:2012, ref:vanderstockt:2018}. Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce. \citet{ref:nel:2021} provides some of the first research in this field, applying \acs{BOHTA}, a novel adaptation of an evolutionary-based \acs{HH}, known as the \acs{AMALGAM} \acs{HH} \citep{ref:vrugt:2007}, to \acs{FFNN} training. Furthermore, \citet{ref:oliva:2019} provide \acs{HHBOA}, the first use of Bayesian optimisation in a \acs{HH} context. The method proposed by \citet{ref:oliva:2019} uses a Bayesian selection operator to evolve combinations of low-level heuristics  while looking for good problem solutions to a benchmark of optimisation functions, but does not apply a \acs{HH} to the training of \acp{FFNN}.

@@

The population state refers to a collection of parameters that are shared between the entities in the population. Population state is also referred to as \textit{global} state and represents the population's memory. The population state generally contains state parameters that are of importance to multiple heuristics, and usually tracks the state of the population and not individual heuristic. Some examples of population state that can arise from different heuristics include the population of entities themselves, the global best entity found so far, the overall best loss achieved thus far, and so on.

@@

All models trained in the empirical process follow implementations of shallow \acp{FFNN} with only one hidden layer. The number of hidden units used were determined empirically. Weights are initialised by means of \textit{Glorot uniform sampling} \citep{ref:glorot:2010}. The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.

@@

The Shapiro-Wilk test for normality \citep{ref:shapiro:1965} ($\alpha$ = 0.001) is used to determine if the results are normally distributed. The Levene's test for equality of variance \citep{ref:levene:1961} ($\alpha$ = 0.001) is used. For experiments with three or more configurations, the \acs{ANOVA} statistical test \citep{ref:fisher:1921} ($\alpha$ = 0.001) is used. The Kruskal-Wallis ranked non-parametric test \citep{ref:kruskal:1952} for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed. Finally, a post-hoc Tukey honest significant difference test \citep{ref:tukey:1949} ($\alpha$ = 0.001) is used from which significant ranking is retrieved. Descriptive and critical difference plots are then retrieved from these results to provide visual aid.

>>>>

Although this research takes a particular interest in training \acp{FFNN}, the \acs{BHH} is not limited to these types of models and can generally be applied to any \acs{ANN} as long as the \acs{ANN} can be trained by all of the low-level heuristics. Experimentation with other \acs{ANN} architectures besides \acp{FFNN} is left for future research.

@@

This research focuses on a particular type of \acs{ANN}, referred to as \acfp{FFNN}. \acp{FFNN} were the first and simplest type of \acp{ANN} developed \citep{ref:schmidhuber:2015} and implement an architecture consisting of input, hidden and output layers by arranging them in sequential order. Furthermore, \acp{FFNN} implement fully connected topologies, where each \acf{AN} in one layer is connected to all the \acp{AN} in the next, without any cycles. In \acp{FFNN}, information moves forward, in one direction, from the input nodes, through the hidden nodes and finally to the output nodes.

@@

There are many variants of gradient-based heuristics. However, they all fundamentally apply the same generic \acs{GD} framework that propagates the error signal backwards through the \acs{ANN}. This algorithm is known as \acf{BP}.

@@

The biggest difference between \acp{MH} and gradient-based heuristics is that \acp{MH} make use of meta-information obtained as a result of evaluating the \acs{FFNN} during training and is not limited to information about the search space \citep{ref:blum:2003}. This also means that \acp{MH} do not necessarily require the error function to be differentiable. \citet{ref:blum:2003} provide advantages of \acp{MH} that include the following: they are easy to implement, they are problem independent and do not require problem-specific knowledge, and they are generally designed to find global optima, while gradient-based approaches can get stuck in local optima more often. Similar to gradient-based heuristics, a number of different meta-heuristics have been used to successfully train \acp{FFNN} \citep{ref:rakitianskaia:2012, ref:vanwyk:2014}. This research takes a particular interest in population-based \acp{MH} that have been used to train \acp{FFNN}. These include \acf{PSO} \citep{ref:abdulkarim:2021}, \acf{DE} \citep{ref:xue:2022}, and \acfp{GA} \citep{ref:khan:2012}.

@@

\citet{ref:burke:2010} propose a classification scheme used to classify \acp{HH}. According to the proposed classification scheme, \acp{HH} are classified in two categories. These include the \textit{source of feedback} used during learning and the nature of the \textit{heuristic search space}. For the category that involves the source of feedback, \acp{HH} can be classified as either \textit{no learning}, \textit{online learning} or \textit{offline learning}. For the category that involves the nature of the \textit{heuristic search space}, \acp{HH} can be classified as either \textit{heuristic selection} or \textit{heuristic generation}. Further distinction is made between \textit{construction} of heuristics and \textit{perturbation} of heuristics.

In the general context of optimisation, many different types of \acp{HH} have been implemented and applied to many different problems. Some notable examples include \citep{ref:burke:2010, ref:grobler:2012, ref:vanderstockt:2018}. Research on the application of \acp{HH} in the context of \acs{FFNN} training is still scarce. \citet{ref:nel:2021} provides some of the first research in this field, applying \acs{BOHTA}, a novel adaptation of an evolutionary-based \acs{HH}, known as the \acs{AMALGAM} \acs{HH} \citep{ref:vrugt:2007}, to \acs{FFNN} training. Furthermore, \citet{ref:oliva:2019} provide \acs{HHBOA}, the first use of Bayesian optimisation in a \acs{HH} context. The method proposed by \citet{ref:oliva:2019} uses a Bayesian selection operator to evolve combinations of low-level heuristics  while looking for good problem solutions to a benchmark of optimisation functions, but does not apply a \acs{HH} to the training of \acp{FFNN}.

@@

The population state refers to a collection of parameters that are shared between the entities in the population. Population state is also referred to as \textit{global} state and represents the population's memory. The population state generally contains state parameters that are of importance to multiple heuristics, and usually tracks the state of the population and not the state of individual heuristics. Some examples of population state that can arise from different heuristics include the population of entities themselves, the global best entity found so far, the overall best loss achieved thus far, and so on.

@@

All models trained in the empirical process follow implementations of shallow \acp{FFNN} with only one hidden layer. The number of hidden units used were determined empirically. Weights are initialised by means of \textit{Glorot uniform sampling}. The models and their configuration, as it is used for each dataset, are given in Table \ref{tab:methodology:models:configurations}.

@@

The Shapiro-Wilk test for normality ($\alpha$ = 0.001) is used to determine if the results are normally distributed. The Levene's test for equality of variance ($\alpha$ = 0.001) is used. For experiments with three or more configurations, the \acs{ANOVA} statistical test ($\alpha$ = 0.001) is used. The Kruskal-Wallis ranked non-parametric test for statistical significance ($\alpha$ = 0.001) is used for cases where data is not normally distributed. Finally, a post-hoc Tukey honest significant difference test ($\alpha$ = 0.001) is used from which significant ranking is retrieved. Descriptive and critical difference plots are then retrieved from these results to provide visual aid.

### 2024-08-15 article/rebuttal_v2/main.tex
💚 For Taylah, Beané & Aleah

\textbf{Title:} Training Feedforward Neural Networks with Bayesian Hyper-Heuristics\\
\textbf{Authors:} A.N. Schreuder, A.S. Bosman, A.P. Engelbrecht, C.W. Cleghorn\\
\textbf{Manuscript number:} 1\\
\textbf{Revision Version:} 1\\
\textbf{Editor’s Decision Received Date:} 24 November 2023\\
\textbf{Revision Submission Date:} 10 January 2024\\

@@

\noindent
The authors would like to thank the editor and reviewers for their constructive comments and suggestions that have helped improve the quality of this manuscript. The manuscript has undergone a thorough revision according to the editor's and reviewer's comments. Please see below our responses. For the editor's and reviewer's convenience, we have highlighted our responses to the comments and described how each comment is addressed in the revised manuscript in \textcolor{blue}{blue}.

@@

\begin{point1}
	Dear authors, I want to apologize for the long process of peer review. We had severe issues to find suitable candidates. The second reviewer keeps ignoring all reminders, so that the decision of the first review round will be based on only a single reviewer. At the same time, I am pleased to inform you that R1 sees merit in your paper, along with several suggestions for further improvement. I wish you good luck in the revision!
\end{point1}

\begin{reply}
	The authors would like to thank the editor and reviewer again for their comments and the time taken to read the manuscript. All the issues raised by the reviewers are addressed in the following document. For each reviewer comment, the corresponding manuscript adjustment is discussed in detail. Where possible, we have highlighted the changes in the revised manuscript in \textcolor{blue}{blue} and provided line numbers for ease of reference.
\end{reply}

\section*{Response to the Reviewers}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\reviewersection
This paper proposes a hyper-heuristic for neural network training. The paper has potential to be accepted, while it needs revision. Some comments in detail are below:

\begin{point}
	In the introduction section, the authors should briefly explain their heuristic. Please again explain the proposed method briefly in this section
\end{point}

\begin{reply}
	We have added a brief overview of the BHH algorithm in the introduction section. Please see the revised manuscript, page 3, lines 29-46.
\end{reply}

\begin{point}
	``This research takes a particular interest in population
	based MHs that have been used to train FFNNs. These include particle
	swarm optimisation (PSO) [20], differential evolution (DE) [21] and genetic
	algorithms (GAs) [22].''\\
	Please add some more recent papers.
\end{point}

\begin{reply}
	We have updated these references to reflect the latest, highly cited journal articles we could find on each of the topics. These include \cite{ref:abdulkarim:2021}, \cite{ref:khan:2012}, and \cite{ref:xue:2022} (See references at the end of this document).
\end{reply}

\begin{point}
	Is there any reasons to select the population size as 5?
\end{point}

\begin{reply}
	A population size of 5 was chosen as it empirically and consistently provided good results. The population size has a lower bound of 4, which is the highest, minimum number of entities required by any low-level heuristic used in this research. Furthermore, our ablation studies \cite{ref:schreuder:2022} have shown that a smaller population size is generally better, since the Bayesian analysis process implemented by the BHH has less, but more concentrated performance information from which it has to learn. We have added a brief discussion on the population size in the revised manuscript. Please see page 20, lines 337-383.
\end{reply}

\begin{point}
	In Figure 3, the points are connected together, while I believe that using a connection between two points is not right! For instance between ``momentum'' and ``de'', there is a connected line. What does mean this connection?
\end{point}

\begin{reply}
	We agree with the comments made and as such we have decided to remove the original Figure 3, since we felt that the figure shows redundant information which is already given in Tables 7 and 8. Furthermore, we felt that the other suggestions made by the reviewer, such as adding classification results, adds more value.
\end{reply}

\begin{point}
	Please provide more classification results such as accuracy!
\end{point}

\begin{reply}
	We have added Tables 9 and 10 which contain classification results as requested. Please see the revised manuscript, pages 31-32.
\end{reply}

\begin{point}
	Please provide a sensitivity analysis on the proposed algorithm?
\end{point}

\begin{reply}
	This is a great suggestion! We have done extensive ablation studies on the BHH algorithm, but originally left this out for brevity. These studies can be found in \cite{ref:schreuder:2022}. We have added a brief discussion and summary of the findings in the ablation studies in the revised manuscript. Please see page 33, lines 542-553.
\end{reply}

\begin{point}
	Can the algorithm extend on other type of ANNs simply?
\end{point}

\begin{reply}
	Yes it can! Although this research takes a particular interest in training FFNNs, the BHH is not limited to these types of models and can generally be applied to any ANN as long as the ANN can be trained by all of the low-level heuristics. Experimentation with other ANN architectures besides FFNNs was left for future research. We have added this context to the introduction section. Please see page 4, lines 57-61.
\end{reply}

>>>>

\textbf{Title:} Training Feedforward Neural Networks with Bayesian Hyper-Heuristics\\
\textbf{Authors:} A.N. Schreuder, A.S. Bosman, A.P. Engelbrecht, C.W. Cleghorn\\
\textbf{Manuscript number:} 1\\
\textbf{Revision Version:} 2\\
\textbf{Editor’s Decision Received Date:} 7 August 2024\\
\textbf{Revision Submission Date:} 16 Aug 2024\\

@@

\noindent
The authors would like to thank the editor and reviewers for their constructive comments and suggestions that have helped improve the quality of this manuscript. The manuscript has undergone a final thorough revision (version 2) according to the editor's and reviewer's comments. Please see below our responses to the latest feedback. For the editor's and reviewer's convenience, we have highlighted our responses to the comments and described how each comment is addressed in the revised manuscript in \textcolor{blue}{blue}.

@@

\begin{point1}
	\begin{itemize}
		\item A thorough editing is required; show all changes made to the revised manuscript.
		\item References: max 50 entries. Make sure the references are recent and highly pertinent to the contents of the manuscript.
	\end{itemize}
\end{point1}

\begin{reply}
	The authors would like to thank the editor and reviewer again for their comments and the time taken to read the manuscript. All the issues raised by the editor/reviewers are addressed in the following document. A number of grammatical and language improvements have been made, and the references are updated and now capped at 49 as requested. A summary of the changes made is given as follows:

	\begin{itemize}
		\item Changed FFNNs to FFNN in the paragraph about the BHH's applicability to different ANN types.

		\item Removed citation ``\citep{ref:zell:1994}'' from the sentence about FFNN topologies.
		\item Removed ``was popularised by \citet{ref:werbos:1994}'' from the sentence about the backpropagation algorithm.
		\item Removed citation ``\citep{ref:gupta:1999}'' from the list of references about meta-heuristics used to train FFNNs.
		\item Changed ``dimensions'' to ``categories'' when describing the classification scheme for hyper-heuristics. Also changed subsequent uses of ``dimension'' to ``category''.
		\item Removed citation ``\citep{ref:dowsland:2007}'' from the list of examples of hyper-heuristics in optimization.
		\item Changed ``not individual heuristic'' to ``not the state of individual heuristics'' when describing what the population state tracks.
		\item Removed citation ``\citep{ref:glorot:2010}'' from the sentence about Glorot uniform sampling for weight initialization.
		\item Removed citations for various statistical tests: Shapiro-Wilk test, Levene's test, ANOVA test, Kruskal-Wallis test, and Tukey honest significant difference test.
	\end{itemize}

\end{reply}
